l

### 2019-12-02 random/career_preparation/resume/resume.tex
cleanup
clean

%-------------------------------------------------------------------------------
%	EDUCATION SECTION
%-------------------------------------------------------------------------------
\section{EDUCATION}
\textbf{University of Chicago}
{\sl B.S.}, Computer Science. \hfill \textbf{Expected Jun, 2021}\\
\textbf{Santa Clara High School} \hfill \textbf{2017}
%-------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%-------------------------------------------------------------------------------
\section{SKILLS}
\textbf{Languages} Python, Julia, C, Bash\\
\textbf{Packages}  PyTorch, Gym, TensorFlow $\geq v2$, Sklearn, Pandas \\
\textbf{Spoken Languages} English - Fluent, Hindi, Spanish, Chinese - Classroom

%-------------------------------------------------------------------------------
% Modify the format of each position
\begin{format}
\title{l}\\
\dates{l}\location{r}\\
\body\\
\end{format}
%-------------------------------------------------------------------------------
\section{EXPERIENCE}
\textbf{Fermilab LSST Intern\hfill Jun 24 - Aug 31}\\
\textbullet{Researched the applications of neural differential equations to astronomy\\}
\textbullet{Used the PLAsTiCC Astronomical Kaggle dataset to train a neural network to approximate the differential equation of different astronomical objects' light curves}\\
\textbullet{Worked with peers and mentors to create a high level API for fast prototyping and ensemble training of neural networks for astronomy datasets, primarily in PyTorch}
\begin{itemize}
    \item \textbf{Technology/Tools:} TorchDiffEq, DifferentialEquations.jl, PyTorch, TensorFlow, Matplotlib, Astropy
\end{itemize}
\section{PROJECTS}
\textbf{Sips: Odds Tracking on GCP\hfill Oct 2018 - Now}\\
\textbullet{Built a python package that tracks sports statistics and odds\\}
\textbullet{Learned about cloud deployment by spinning up free-tier VMs on GCP\\}
\textbullet{Have collected over 1 GBs of live odds data from football, basketball and hockey}\\
\textbullet{Long-Short Term Memory (LSTM) classifer for directional movement of moneyline}
\begin{itemize}
\item \textbf{Technology/Tools:} Python, Requests, Beautiful Soup, PyTorch
\end{itemize}
\begin{itemize}
\item \textbf{Link :} github.com/anandijain/sips
\end{itemize}
\textbf{Gym-Sips: RL Gym Environment\hfill Feb 2019 - Now}\\
\textbullet{Created a set of custom reinforcement learning environments using the OpenAI Gym package for the output of Sips\\}
\textbullet{Attempted to use a Deep-Q network to learn a state value function.\\}
\textbullet{Goal: I'd like to update my envs to be compatible with TF-agents and run the different algorithms supported and see if the agent learns any better}

\begin{itemize}
\item \textbf{Technology/Tools:} Python, Gym, PyTorch
\end{itemize}
\begin{itemize}
\item \textbf{Link :} github.com/anandijain/gym-sips
\end{itemize}

@@

\textbf{UCQuantum\hfill Aug 2019 - Now}\\
\textbullet{Unofficial club applying to become an official RSO for UChicago undergrads interested in quantum computing}\\
\textbullet{We have 50 facebook group members and roughly 15 active members}\\
\textbullet{Initial meetings have been learning/teaching the basics: superposition, entanglement, quantum logic gates, unitary matrices, and superdense coding}\\
\textbullet{We are planning to host talks, hackathons, and lab tours with faculty on campus}\\
%-------------------------------------------------------------------------------

>>>>

%-------------------------------------------------------------------------------
%	EDUCATION SECTION
%-------------------------------------------------------------------------------
\section{EDUCATION}
\textbf{University of Chicago}
{\sl B.S.}, Computer Science. \hfill \textbf{Expected Jun, 2021}\\
\textbf{Santa Clara High School} \hfill \textbf{2017}
%-------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%-------------------------------------------------------------------------------
\section{SKILLS}
\textbf{Languages:} Python, Julia, Bash, C\\
\textbf{Packages:}  PyTorch, Gym, TensorFlow, Scikit-Learn, Pandas \\
\textbf{Spoken:} English, Hindi, Spanish

%-------------------------------------------------------------------------------
% Modify the format of each position
\begin{format}
\title{l}\\
\dates{l}\location{r}\\
\body\\
\end{format}
%-------------------------------------------------------------------------------
\section{EXPERIENCE}
\textbf{Fermilab LSST Intern\hfill Jun 24 - Aug 31}\\
\textbullet{Researched the applications of neural differential equations to astronomy\\}
\textbullet{Used the PLAsTiCC Astronomical Kaggle dataset to train a neural network to approximate the differential equation of different astronomical objects' light curves}\\
\textbullet{Worked with peers and mentors to create a high level API for fast prototyping and ensemble training of neural networks for astronomy datasets, primarily in PyTorch}
\begin{itemize}
    \item \textbf{Technology/Tools:} TorchDiffEq, DifferentialEquations.jl, PyTorch, TensorFlow, Matplotlib, Astropy
\end{itemize}
\section{PROJECTS}
\textbf{Sips: Sports Data Tool on Google Cloud\hfill Oct 2018 - Now}\\
\textbullet{Package to track odds and player data from a variety of sports and sources\\}
\textbullet{Have collected over 1 GBs of live odds data from football, basketball and hockey}\\
\textbullet{Example prediction models using TensorFlow, including classification and LSTM prediction models}
\begin{itemize}
\item \textbf{Technology/Tools:} Python, Requests, Beautiful Soup, TensorFlow
\end{itemize}
\begin{itemize}
\item \textbf{Link :} github.com/anandijain/sips
\end{itemize}
\textbf{Gym-Sips: Reinforcement Learning Environment\hfill Feb 2019 - Now}\\
\textbullet{Custom reinforcement learning environments using the OpenAI Gym package for the output data of sips}

\begin{itemize}
\item \textbf{Technology/Tools:} Python, Gym, TensorFlow, TF-Agents
\end{itemize}
\begin{itemize}
\item \textbf{Link :} github.com/anandijain/gym-sips
\end{itemize}

@@

\textbf{UCQuantum (.org)\hfill Aug 2019 - Now}\\
\textbullet{Unofficial club applying to become an official RSO for UChicago undergrads interested in quantum computing}\\
\textbullet{We have 50 facebook group members and 10 active members}\\
\textbullet{We are planning to host talks, hackathons, and lab tours with faculty on campus}\\
%-------------------------------------------------------------------------------
